A Large-Scale Study of the Use of Eval in R

### 2020-08-27 inst/paper/main.tex
Add implementation usage scenario

@@

>>>>

In the corpus, we observe \AllEventCountRnd events. Only \EvalEventCountRnd
events occur inside eval. This is just \EvalEventAllPerc of all events.
Figure~\ref{fig:event-distribution} shows the distribution of events for
core and package \eval calls.

@@

  \subsubsection{Implementation}
  The package installation process adds an extra file to the package directory
  that contains the code to load the package code inside a \local block. It
  creates a namespace object and injects the package bindings.
